Automating Verification of MPC Security

### 2023-06-03 popl24/minicat.tex
checkpoint

>>>>

\paragraph{Variable and Memory Conventions} Given a program $\prog$, we
write $\iov(\prog)$ to denote the pair $(S,V)$
where $S$ is the set of secret variables in $\prog$ and
$V$ is the set of views in $\prog$, and we write $\flips(\prog)$ to
denote the set $F$ of flip variables in $\prog$. For any set of variables $X$
and parties $P$, we write $X_P$ to denote the subset
of $X$ owned by any party in $P$, and we write $X_H$ and
$X_C$ to denote the subsets belonging to honest and
corrupt parties, respectively.

Given a set of variables $X$, we write $\store_X$ to mean the memory
$\store$ restricted to the domain $X$, and
and we define $\mems(X)$ as:
$$
\mems(X) \defeq \{ \store \mid \dom(\store) = X \}
$$
We will also write $\store_1 \cup \store_2$ to denote
the memory resulting by combining disjoint
memories $\store_1$ and $\store_2$, i.e.,
under the assumption that $\dom(\store_1) \cap \dom(\store_2) = \varnothing$.
